\section{Support for mobility}

%10.1
\subsection{Why is strong consistency of file systems problematic in a wireless and mobile
environment? What are the alternatives?}

%10.2
\subsection{How do conventional file systems react to disconnected systems? Try unplugging a
computer that has mounted a file system via a network.}

%10.3
\subsection{What advantages has the statelessness of HTTP? In what situations is state useful
and how is it provided today? Where is long-term state stored, where short-term?}

%10.4
\subsection{Which properties of HTTP waste bandwidth? What is the additional problem using
HTTP/1.0 together with TCP? How does HTTP/1.1 improve the situation?}

%10.5
\subsection{How does caching improve access time and reduce bandwidth requirements? What
are locations for a cache and their specific advantages?}

%10.6
\subsection{What are problems of caches in real life? What type of content can be cached, which
content causes problems? What are the additional problems with client mobility?}

%10.7
\subsection{What discrepancies exist between the possibilities of HTML and the realities of
wireless handheld devices? What are proposed solutions? What is the role of plug-ins
today and how do they influence the usability of web pages?}

%10.8
\subsection{Name mechanisms to improve web access for handheld devices. What is their
common problem and what led finally to the development of WAP?}

%10.9
\subsection{What are typical enhancements to the basic client/server architecture of the web?
Reconsider these enhancements for a mobile wireless user with web access over a
mobile phone network. What are efficient locations for the enhancements?}

%10.10
\subsection{What are the primary goals of the WAP Forum efforts and how are they reflected in
the initial WAP protocol architecture?}

%10.11
\subsection{What migration paths does WAP 1.x offer for Internet and telephony applications and
their protocols? Compare with WAP 2.0.}

%10.12
\subsection{Is WDP a fixed protocol and why does WAP not define a SAP which WDP can use?}

%10.13
\subsection{Why does WAP define its own security layer and does not rely on the security
provided by the mobile phone network? What problems does the WAP security layer
cause? Think of end-to-end security.}

%10.14
\subsection{Name the advantages and disadvantages of user acknowledgements in WTP. What
are typical applications for both cases?}

%10.15
\subsection{Which WTP class reflects the typical web access best? How is unnecessary
overhead avoided when using WSP on top of this class for web browsing?}

%10.16
\subsection{What problems of HTTP can WSP solve? Why are these solutions especially needed
in wireless mobile environments?}

%10.17
\subsection{Why does WSP/B not put responses into the same order as the requests? Think, for
example, of requests for different items on a web page.}

%10.18
\subsection{What advantages does a connectionless session service offer compared to a simple
datagram service?}

%10.19
\subsection{What are the enhancements of WAE to the classic client/server model of the web?
What are functions of this enhancement?}

%10.20
\subsection{What is the fundamental difference of WML compared to HTML? Why can this
difference be important with respect to handheld devices? What is specified in
addition to save bandwidth?}

%10.21
\subsection{Why has a scripting language been added to WML? How can this language help
saving bandwidth and reducing delay?}

%10.22
\subsection{What are typical telephony events and how are they integrated into WAP? How can a
user access features of mobile phones via the web browser?}

%10.23
\subsection{What is the role of a WTA server? What are the different ways of integrating WTA
servers into the WAP architecture?}

%10.24
\subsection{What is the difference between WAP service indication and service loading? What
applications could use these services? What is a push good for anyway?}

%10.25
\subsection{Name key differences between WAP 1.x and i-mode. What were problems in the
early WAP days and why was i-mode that successful in Japan?}

%10.26
\subsection{Why is a common synchronisation framework useful? What problems remain?}

%10.27
\subsection{What are major differences between WAP 2.0 and WAP 1.x? What influenced the
WAP 2.0 development?}

%10.28
\subsection{Compare the presented protocol stacks for WAP 2.0 and give application examples.}




